\documentclass[a4paper,11pt]{article}
\RequirePackage[T1]{fontenc}

\usepackage{times}
\usepackage{calc}
\usepackage[shortcuts]{extdash}

\usepackage{graphicx} 

\reversemarginpar

\usepackage[paper=letterpaper,
            marginparwidth=1.1in,     % Length of section titles
            marginparsep=.095in,       % Space between titles and text
            margin=0.5in,               % 1 inch margins
            tmargin=0.65in,
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{0em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin=\bibhang,%
        itemindent=-\bibhang,
        itemsep=\bibsep,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=[\arabic*],resume,leftmargin={\bibhang+\widthof{[999]}},%
        itemindent=-\bibhang,
        itemsep=0.05in,parsep=\z@,partopsep=0pt,
        topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\renewcommand{\section}[1]{\pagebreak[3]%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\hyphenpenalty=10000\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

\newcommand*\fixendlist[1]{%
    \expandafter\let\csname preFixEndListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixEndListend#1\endcsname\vspace{-0.6\baselineskip}}}

\let\originalItem\item
\newcommand*\fixouterlist[1]{%
    \expandafter\let\csname preFixOuterList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\def\item{\pagebreak[2]\oldItem}\csname preFixOuterList#1\endcsname}
    \expandafter\let\csname preFixOuterListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\let\item\oldItem\csname preFixOuterListend#1\endcsname}}
\newcommand*\fixinnerlist[1]{%
    \expandafter\let\csname preFixInnerList#1\expandafter\endcsname\csname #1\endcsname
    \expandafter\def\csname #1\endcsname{\let\oldItem\item\let\item\originalItem\csname preFixInnerList#1\endcsname}
    \expandafter\let\csname preFixInnerListend#1\expandafter\endcsname\csname end#1\endcsname
    \expandafter\def\csname end#1\endcsname{\csname preFixInnerListend#1\endcsname\let\item\oldItem}}

\newlist{outerlist}{itemize}{3}
    \setlist[outerlist]{label=\enskip\textbullet,leftmargin=*}
    \fixendlist{outerlist}
    \fixouterlist{outerlist}

\newlist{lonelist}{itemize}{3}
    \setlist[lonelist]{label=\enskip\textbullet,leftmargin=*,partopsep=0pt,topsep=0pt}
    \fixendlist{lonelist}
    \fixouterlist{lonelist}

\newlist{innerlist}{itemize}{3}
    \setlist[innerlist]{label=\enskip\textbullet,leftmargin=*,parsep=1pt,itemsep=2pt,topsep=0pt,partopsep=0pt}
    \fixinnerlist{innerlist}

\newlist{loneinnerlist}{itemize}{3}
    \setlist[loneinnerlist]{label=\enskip\textbullet,leftmargin=*,parsep=0pt,itemsep=2pt,topsep=0pt,partopsep=0pt}
    \fixendlist{loneinnerlist}
    \fixinnerlist{loneinnerlist}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\usepackage{doi}
\usepackage{url}

\urlstyle{same}
\providecommand*\emaillink[1]{\nolinkurl{#1}}
\providecommand*\email[1]{\href{mailto:#1}{\emaillink{#1}}}

\begin{document}

 {\hspace*{-\marginparsep minus \marginparwidth}%
\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
\centering
% {\LARGE \bfseries {Kexin Quan}}\\
\vspace{0.2cm}
% \href{mailto:vanvuong.trinh@gmail.com}{\texttt{kequan@ucsd.com}} \\
% \href{https://trinhvv.github.io}{\texttt{http://trinhvv.github.io}}
% \rule{\columnwidth}{1.2pt}
\begin{center}
    \textbf{\Huge \scshape Kexin Quan} \\ \vspace{6pt}
    \href{mailto:kq4@illinois.edu}{\underline{kq4@illinois.edu}} $|$
    \href{https://www.linkedin.com/in/kexinquan/}{\underline{LinkedIn}} $|$
    \href{https://scholar.google.com/citations?user=XrAI6c8AAAAJ&hl=en}{\underline{Google Scholar}} $|$
    \href{https://www.kexinquan.com/}{\underline{kexinquan.com}} \\
    \vspace{3pt}
    \textbf{Availability: May--August 2026}
\end{center}
\end{minipage}}

\section{Focus}

Building experimentation and measurement products that help users understand their true business value. I design AI-powered systems with rigorous A/B testing, define success metrics, and partner with cross-functional teams (Engineering, Design, Data Science) to ship data-driven products. Published 10+ papers at CHI/C\&C on product effectiveness and user behavior measurement.

 \section{Education}

\textbf{Ph.D. in progress, Information Sciences} University of Illinois, Urbana-Champaign
\hfill {2023-2028}\\
\textit{Supervised by Prof. Jessie Chin}

\textbf{M.S. Electrical \& Computer Eng} University of California, San Diego 
\hfill {2021-2023}\\
\textit{Machine Learning and Data Science}
% \textit{Overall GPA: 3.70}

\vspace{0.1cm}

\textbf{B.S. Cognitive Science} 
University of California, San Diego
\hfill {2017-2021}\\
\textit{Specialization in Machine Learning \& Neural Computation}
% \textit{Overall GPA: 3.69, Major GPA: 3.97}

\section{Publications}
\begin{bibenum}

\item \href{https://arxiv.org/abs/2510.23904}{\textbf{K. Quan}, D. Albassam\textsuperscript{$\dagger$}, M. Wu\textsuperscript{$\dagger$}, Z. Ding, J. Chin. Towards AI as Colleagues: Multi-Agent System Improves Structured Ideation Processes. 
\emph{In Proceedings of the 2026 CHI Conference on Human Factors in Computing Systems (CHI ’26). (Accepted)} }
\label{multicolleagues}

\item \href{https://arxiv.org/abs/2602.14467}{\textbf{K. Quan}, J. Chin. Conversational Decision Support for Information Search Under Uncertainty: Effects of Gist and Verbatim Feedback.
\emph{International Journal of Human-Computer Studies (Under Review), 2026}}
\label{sera}

\item \href{https://arxiv.org/abs/2509.11115}{M. Wu, \textbf{K. Quan}, W. Liu, M. Yao, J. Chin. "Pragmatic Tools or Empowering Friends?" Discovering and Co-Designing Personality-Aligned AI Writing Companions.
\emph{In Proceedings of the 2026 Conference Creativity and Cognition (C\&C’26), London, UK. (In Submission)} }
\label{mbti}


\item \href{https://arxiv.org/pdf/2511.02428}{M. Bak, \textbf{K. Quan}, T. Tomaszewski, J. Chin. Can Conversational AI Counsel for Change? A Theory-Driven Approach to Supporting Dietary Intentions in Ambivalent Individuals.
\emph{arXiv preprint arXiv:2511.02428 (2025)}.}
\label{counsel_llm}



\item \href{https://dl.acm.org/doi/10.1145/3698061.3734388}
{\textbf{K. Quan}, P. Ramakrishnan, J. Chin. Can AI Take a Joke—Or Make One? A Study of Humor Generation and Recognition in LLMs. 
\emph{In Adjunct Proceedings of the 2025 Conference on Creativity and Cognition (C\&C’25), Online, 2025.} }
\label{llm_humor}

\item \href{https://dl.acm.org/doi/10.1145/3706599.3720185}
{M. Wu, \textbf{K. Quan}, W. Liu, M. Yao, J. Chin. Incorporating Personality into AI Writing Companions: Mapping the Design Space. 
\emph{ In Adjunct Proceedings of the CHI Conference on Human Factors in Computing Systems Extended Abstracts (CHI EA '25). ACM. Late-Breaking Work. } }
\label{chilbw}

\item \href {https://dl.acm.org/doi/abs/10.1145/3591196.3596818}
{Z. Huang, \textbf{K. Quan,} J. Chan, S. MacNeil. CausalMapper: Challenging designers to think in systems with Causal Maps and Large Language Model.
\emph{In Adjunct Proceedings of the 15th Conference on Creativity and Cognition (C\&C’23), Online, 2023.} }
\label{causalmapper}

% \item \href{https://dl.acm.org/doi/fullHtml/10.1145/3544548.3581393}
% {Q. Yang, Y. Hao\textsuperscript{$\dagger$}, \textbf{K. Quan\textsuperscript{$\dagger$}}, S. Yang\textsuperscript{$\dagger$}, Y. Zhao\textsuperscript{$\dagger$}, V. Kuleshov, F. Wang. 2023. Harnessing Biomedical Literature to Calibrate Clinicians’ Trust in AI Decision Support Systems.
% \emph{In Proceedings of the 2023 CHI Conference on Human Factors in Computing Systems (CHI’23).} }
\item \href{https://dl.acm.org/doi/fullHtml/10.1145/3544548.3581393}
{Q. Yang, Y. Hao\textsuperscript{$\dagger$}, \textbf{K. Quan\textsuperscript{$\dagger$}}, S. Yang\textsuperscript{$\dagger$}, Y. Zhao\textsuperscript{$\dagger$}, V. Kuleshov, F. Wang. 2023. Harnessing Biomedical Literature to Calibrate Clinicians’ Trust in AI Decision Support Systems.
\emph{In Proceedings of the 2023 CHI Conference on Human Factors in Computing Systems (CHI’23).}}
\footnotetext{\textsuperscript{$\dagger$}Co-second authors with equal contribution.}
\label{calibrate_trust}

\item \href{https://dl.acm.org/doi/abs/10.1145/3450741.3465261}{S. MacNeil, Z. Ding, \textbf{K. Quan,} T. J. Parashos, Y. Sun, S. P. Dow. Creative Work: Helping Novices Frame Better Problems through Interactive Scaffolding.
\emph{In Proceedings of the 13th Conference on Creativity and Cognition (C\&C’21), Online, 2021.}}
\label{problib}

% https://dl.acm.org/doi/10.1145/3474349.3480203
\item \href{https://dl.acm.org/doi/10.1145/3474349.3480203}{S. MacNeil, Z. Ding, \textbf{K. Quan,} Z. Huang, K. Chen, S. P. Dow. ProbMap: Automatically Constructing Design Galleries through Feature Extraction and Semantic Clustering.
\emph{In Adjunct Proceedings of the 2021 Annual ACM Symposium on User Interface Software and Technology (UIST’21 Demo), Online, 2021.} }
\label{probmap}

\end{bibenum}

% \textsuperscript{$\dagger$}Co-second authors with equal contribution.


\section{Research Experience}

\textbf{Graduate Research Assistant},
{UIUC School of Information Sciences}
\hfill {July 2023--present}
\begin{innerlist}
\item Led end-to-end development of AI-powered decision support products: defined product requirements, wrote technical specs, set success metrics, and shipped to 100+ users across multiple studies.

\item Designed and executed controlled experiments (A/B tests, within-subject designs) with 100+ participants to measure product impact on user behavior, analyzing results to inform product strategy and iteration.

\item Collaborated cross-functionally with Engineering, Design, and Data Science teams to develop, test, and launch 3 AI products, including a multi-agent ideation platform and a decision-support assistant.

\item Defined success metrics and analyzed data to drive product prioritization---measured engagement, task completion, and user satisfaction using SQL, Python, and statistical modeling.
\end{innerlist}
\vspace{0.2cm}

\textbf{Visiting Research Intern},
{Cornell DesignAI Group}
\hfill {Mar 2022--Sep 2022}
\begin{innerlist}
\item Built and shipped a clinical decision-support product integrating AI recommendations with biomedical literature to help clinicians evaluate treatment options.
\item Conducted user research through clinician interviews to validate product-market fit and iterate on UX, contributing to a CHI'23 full paper \ref{calibrate_trust}.
\item Wrote product requirements and technical specs for development team, coordinating design iterations across stakeholders.
\end{innerlist}
\vspace{0.2cm}

\textbf{Research Assistant},
{UCSD Design Lab}
\hfill {Apr 2020--Aug 2021}
\begin{innerlist}
\item Built real-time data pipeline processing 300+ users' unstructured inputs using NLP to enable feature extraction and semantic clustering for product personalization.
\item Developed creativity-support tools deployed to 80+ users, iterating based on user feedback and behavioral analytics (C\&C'21 \ref{problib}, UIST'21 \ref{probmap}).
\item Defined metrics and analyzed user behavior data to drive product improvements and validate design decisions.
\end{innerlist}

\section{Industry Experience}
\textbf{Data Analyst Intern},
{Axos Bank, San Diego, CA}
\hfill{May--Aug 2021}
\begin{innerlist}
\item Built measurement dashboard (SQL, Python, Excel) to track consumer deposit metrics across product lines in real-time, enabling data-driven decisions for deposit strategy team.
\item Analyzed user behavior patterns to identify overdraft risk factors; developed targeted intervention strategy that reduced overdraft incidence among 60\% of business banking customers.
\item Defined success metrics and measured impact: automated review workflows, cutting manual workload by 5.7\% and generating \$23K additional annual revenue.
\end{innerlist}


\section{Skills}

\textbf{Product \& Strategy:}{ Product Roadmaps, PRDs, Technical Specs, Success Metrics, A/B Testing Design, User Research}

\textbf{Data \& Experimentation:}{ SQL, Python, R, Statistical Analysis, Causal Inference, Hypothesis Testing, Pandas}

\textbf{ML \& Analytics:}{ TensorFlow, PyTorch, scikit-learn, NLP (spaCy, NLTK), LLM APIs (OpenAI, Claude)}

\textbf{Visualization:}{ Tableau, Plotly, Matplotlib, Seaborn, Data Storytelling}

\textbf{Tools:}{ Figma, Miro, Firebase, Git, React.js, Cursor, Claude Code, GitHub Copilot}


\section{Leadership \& Service}

\textbf{Publication Chair}, ACM Creativity \& Cognition (C\&C) 2026 --- Led cross-functional coordination for conference proceedings

\textbf{Reviewer}, ACM CHI, C\&C (15+ papers) \hfill{2024--2026}

\textbf{Mentor}, 4 undergraduate/master students on AI product research projects \hfill{2024--present}






%\halfblankline

\end{document}

